Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-09-12 paper.tex
Add files via upload

The bulk of the CRps are injected by relatively low Mach number shocks
and parametrized by $f_\rmn{p,inj}(p) =
C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
2.5$ in our simulations. The CRps approximately trace the thermal gas
with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed
by the injected CR energy in the last 650~Myrs. Our simulations show
that it approximately amounts to 0.03 per cent of the thermal energy inside
the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{CR,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
that the injected energy in the last 650 Myr is smaller by about a factor of 10
in comparison to the cumulative CR energy injected over the entire cosmological
history of the cluster, but this component is nonetheless important since above
1 GHz the radio emission is dominated by CRes injected during the merger, which
have not yet had time to cool.  Similarly, the initial CRe distribution is given
by the steady state between cooling (Coulomb, inverse Compton, and synchrotron)
and injection of secondary CRes from $f_\rmn{p,0}$.  The diffusion constant
$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha_{\rm tu}-1} \sqrt{T} k_L$ is
calculated for each radial bin. All parameters and assumptions are similar to
what is used for our simulated cluster (see section~\ref{sec:results}). Our
fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm
  CR, spat}=1.0$, and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also
assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.

@@

\C{It is
  interesting to reconsider surface brightness and spectral profiles if indeed
  $\tau_{\rm D} \sim \tau_{\rm cl}$ for the reasons mentioned above (e.g.,
  equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting such an
  ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
  Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}$, $\alpha_{\rm tu}$, and
  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const} is adopted, the radial behaviour of $\tau_{\rm cl}$ is
      also modified. Because $\tau_{\rm D}$ decreases with radius (see
      e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease by the same
      amount, which results in a steeper radio profile. To compensate for this
      effect in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR,
        spat}=1.0\rightarrow0.5$ and decrease the relative CR-to-thermal energy
      within the virial radius by a factor five to $6\times10^{-4}$.}} Instead
  of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm
    cl}/\tau_{\rm D} = 2.5 $. The results are remarkably revealing. In this case, we are indeed less
  sensitive to the properties of the turbulence, and more sensitive to the
  details of the CR seed population.  This gives hope to the possibility that
  one could effectively marginalise over the very uncertain properties of
  turbulence at larger scales in merging clusters (which are unlikely to be more
  precisely constrained observationally in the near future) to learn something
  about the underlying CR population.}

@@

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{figure7_prof.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{figure7_spec.eps}
   \end{center}
\end{minipage}
\caption{\C{Sensitivity of radio emission in the Coma cluster to critical
    parameters when we vary the ratio of the time scales on which turbulence is
    active ($\tau_{\rm cl}$) to the turbulent re-acceleration time ($\tau_{\rm
      D}$). In comparison to Figure~\ref{fig:param_comp}, we change our fiducial
    model (solid lines) and adopt a slightly more extended spatial distribution
    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the CR-to-thermal energy by a
    factor of five; otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
    $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values and vary each parameter
    separately in each row of panels. Radio surface brightness profiles (left)
    are contrasted to radio synchrotron spectra (right; for more details see
    caption to Figure~\ref{fig:param_comp}).  Provided there is a minimum
    (threshold) level of turbulence ($X_\rmn{tu}\gtrsim0.2$), here the radio
    profiles are mainly determined by the CR distribution, while turbulence
    has a smaller impact. In the bottom two panels we vary the exponential
    momentum growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see
    equations~\ref{eq:pexp} and \ref{eq:Creacc}), which mainly changes the
    normalisation of the CR distribution and neither spectral shape nor radial
    synchrotron profile. Interestingly, the flat CR profiles adopted here are
    similar to those required to reproduce the radio profiles in our CR
    streaming model (see Figure~\ref{fig:sync_profile}).}}
  \label{fig:param_comp_tcl_tD}
\end{figure*}

>>>>

The bulk of the CRps are injected by relatively low Mach number shocks
and parametrized by $f_\rmn{p,inj}(p) =
C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
2.5$ in our simulations. The CRps approximately trace the thermal gas
with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed
by the \AP{injection rate of} CR energy in the last 650~Myrs. Our simulations show
that \AP{the energy} approximately amounts to 0.03 per cent of the thermal energy inside
the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{CR,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
that the injected energy in the last 650 Myr is smaller by about a factor of 10
in comparison to the cumulative CR energy injected over the entire cosmological
history of the cluster. \AP{However, since the average injection rates of CR energy are similar, 
the CRes injected during the merger are especially important for the radio emission above 1 GHz 
since these CRs have not yet had time to cool.}  Similarly, the initial CRe distribution is given
by the steady state between cooling (Coulomb, inverse Compton, and synchrotron)
and injection of secondary CRes from $f_\rmn{p,0}$.  The diffusion constant
$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha_{\rm tu}-1} \sqrt{T} k_L$ is
calculated for each radial bin. All parameters and assumptions are similar to
what is used for our simulated cluster (see section~\ref{sec:results}). Our
fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm
  CR, spat}=1.0$, and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also
assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.

@@

\C{It is
  interesting to reconsider surface brightness and spectral profiles if indeed
  $\tau_{\rm D} \sim \tau_{\rm cl}$ for the reasons mentioned above (e.g.,
  equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting such an
  ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
  Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}$, $\alpha_{\rm tu}$, and
  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When \C{$\tau_{\rm cl}/\tau_{\rm decay} \sim$const} is adopted, the radial behaviour of $\tau_{\rm cl}$ is
      also modified. Because $\tau_{\rm D}$ decreases with radius (see
      e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease by the same
      amount, which results in a steeper radio profile. To compensate for this
      effect in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR,
        spat}=1.0\rightarrow0.5$ and \AP{decrease the injection rate of CR energy by a factor five.}}} Instead
  of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm
    cl}/\tau_{\rm D} = 2.5 $. The results are remarkably revealing. In this case, we are indeed less
  sensitive to the properties of the turbulence, and more sensitive to the
  details of the CR seed population.  This gives hope to the possibility that
  one could effectively marginalise over the very uncertain properties of
  turbulence at larger scales in merging clusters (which are unlikely to be more
  precisely constrained observationally in the near future) to learn something
  about the underlying CR population.}

@@

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{figure7_prof.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{figure7_spec.eps}
   \end{center}
\end{minipage}
\caption{\C{Sensitivity of radio emission in the Coma cluster to critical
    parameters when we vary the ratio of the time scales on which turbulence is
    active ($\tau_{\rm cl}$) to the turbulent re-acceleration time ($\tau_{\rm
      D}$). In comparison to Figure~\ref{fig:param_comp}, we change our fiducial
    model (solid lines) and adopt a slightly more extended spatial distribution
    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the \AP{injection rate of CR energy by a factor five}; 
    otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
    $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values and vary each parameter
    separately in each row of panels. Radio surface brightness profiles (left)
    are contrasted to radio synchrotron spectra (right; for more details see
    caption to Figure~\ref{fig:param_comp}).  Provided there is a minimum
    (threshold) level of turbulence ($X_\rmn{tu}\gtrsim0.2$), here the radio
    profiles are mainly determined by the CR distribution, while turbulence
    has a \AP{remarkable} small impact. In the bottom two panels we vary the exponential
    momentum growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see
    equations~\ref{eq:pexp} and \ref{eq:Creacc}), which mainly changes the
    normalisation of the CR distribution and neither spectral shape nor radial
    synchrotron profile. Interestingly, the flat CR profiles adopted here are
    similar to those required to reproduce the radio profiles in our CR
    streaming model (see Figure~\ref{fig:sync_profile}).}}
  \label{fig:param_comp_tcl_tD}
\end{figure*}
